\bf Brother, Can You Spare a Manufacturing Job? White Voter Reactions to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd
draft.rmd

---
title: 'bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization'
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

```{r setup, echo=F, message = F, warning= F}
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(readxl)
library(scales)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

@@

# state shapefile
county_shape <- counties(
  cb = TRUE,
  resolution = "20m"
) %>%
  shift_geometry() %>%
  mutate(STATEFP = as.numeric(STATEFP),
         COUNTYFP = as.numeric(COUNTYFP))

state_shape <- states(
  cb = TRUE,
  resolution = "20m"
) %>%
  filter(GEOID != "72") %>%
  shift_geometry()

@@

    # calculate the counterfactual change in democratic vote share
    # by multipling our regression coefficient against the difference
    # between observed manufacturing layoffs (our measure) and the
    # 25th percentile of layoffs (nationally)
         CF_netchange = p25,
         CF_d_netchange = CF_netchange - mfgNetChange_white,
         CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
         P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
  dplyr::select(id, state_fips, state, state_name, county_fips,
                county, year, dem_votes_pct1, ddem_votes_pct1,
                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
                mfgNetChange_nonwhite,
                CF_netchange,
                CF_d_netchange,
                CF_ddem_change,
                P_ddem_2)

@@

# state shapefile
state_shape <- states(
  cb = TRUE,
  resolution = "20m"
) %>%
  filter(GEOID != "72") %>%
  shift_geometry()

@@

#devtools::install_github("yutannihilation/ggsflabel")
library(ggsflabel)

@@

### example state: Michigan

### 2020

>>>>

---
title: '\bf Brother, Can You Spare a Manufacturing Job? White Voter Reactions to Deindustrialization'
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

```{r setup, echo=F, message = F, warning= F}
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(readxl)
library(scales)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

@@

# state shapefile
county_shape <- counties(
  cb = TRUE,
  resolution = "20m",
  progress_bar = F
) %>%
  shift_geometry() %>%
  mutate(STATEFP = as.numeric(STATEFP),
         COUNTYFP = as.numeric(COUNTYFP))

state_shape <- states(
  cb = TRUE,
  resolution = "20m",
  progress_bar = F
) %>%
  filter(GEOID != "72") %>%
  shift_geometry()

@@

    # calculate the counterfactual change in democratic vote share
    # by multiplying our regression coefficient against the difference
    # between observed manufacturing layoffs (our measure) and the
    # 25th percentile of layoffs (nationally)
         CF_netchange = p25,
         CF_d_netchange = CF_netchange - mfgNetChange_white,
         CF_ddem_change = CF_d_netchange*model_results$coefficients[1],
         P_ddem_2 = P_ddem_1 + CF_ddem_change) %>%
  dplyr::select(id, state_fips, state, state_name, county_fips,
                county, year, dem_votes_pct1, ddem_votes_pct1,
                P_ddem_1, mfgNetChange_white, mfgNetChange_total,
                mfgNetChange_nonwhite,
                CF_netchange,
                CF_d_netchange,
                CF_ddem_change,
                P_ddem_2)

@@

# state shapefile
state_shape <- states(
  cb = TRUE,
  resolution = "20m",
  progress_bar = F
) %>%
  filter(GEOID != "72") %>%
  shift_geometry()

@@

# devtools::install_github("yutannihilation/ggsflabel")
library(ggsflabel)

@@
